ICBEdataset_paper_figure_prep

### 2022-02-04 replication_data/rmd/01_compile_saves_and_align.Rmd
Consolidated save files, names, and locations

save dataset with alignment
```{r}
saveRDS(icb_wide_aligned %>% dplyr::arrange(savefile_crc32, sentence_number_int, event_number_int),
     file=paste0(here::here(),"/replication_data/out/icb_coder_crisis_sentence_event_aligned.Rds"))
```

>>>>

save dataset with alignment
```{r}
saveRDS(icb_wide_aligned %>% dplyr::arrange(savefile_crc32, sentence_number_int, event_number_int),
     file=paste0(here::here(),"/replication_data/temp/ICBe_V1_long_unclean.Rds"))
```

### 2022-02-04 replication_data/rmd/02_format_and_clean.rmd
Consolidated save files, names, and locations

read in icb_coder_crisis_sentence_event_aligned.Rds
```{r}
icb_wide_aligned_raw <- readRDS(file=paste0(here::here(),"/replication_data/out/icb_coder_crisis_sentence_event_aligned.Rds")) %>% 
                    dplyr::mutate(crisno3 = stringr::str_pad(crisno, 3, pad = "0"), sentence_number_int_aligned3 =
                                    stringr::str_pad(sentence_number_int_aligned, 3, pad = "0")) %>%
                    dplyr::mutate(email_crisis_sent_event =
                                    paste0(email_id,"_",crisno3,"_",sentence_number_int_aligned3,"_",event_number_int)) %>%
                    dplyr::select(-crisno3, -sentence_number_int_aligned3) %>%
                    dplyr::arrange(crisno, sentence_number_int, event_number_int) %>%

@@

Save icb_long_clean!
```{r}
saveRDS(icb_long_clean_final, paste0(here::here(), "/replication_data/temp/icb_long_clean.Rds"))
saveRDS(icb_long_clean_final, paste0(here::here(), "/replication_paper/data/in/icb_long_clean.Rds"))

@@

saveRDS(icb_wide_clean, paste0(here::here(), "/replication_data/temp/icb_wide_clean.Rds")) 
saveRDS(icb_wide_clean, paste0(here::here(), "/replication_paper/data/in/icb_wide_clean.Rds"))

>>>>

read in icb_coder_crisis_sentence_event_aligned.Rds
```{r}
icb_wide_aligned_raw <- readRDS(file=paste0(here::here(),"/replication_data/temp/ICBe_V1_long_unclean.Rds")) %>% 
                    dplyr::mutate(crisno3 = stringr::str_pad(crisno, 3, pad = "0"), sentence_number_int_aligned3 =
                                    stringr::str_pad(sentence_number_int_aligned, 3, pad = "0")) %>%
                    dplyr::mutate(email_crisis_sent_event =
                                    paste0(email_id,"_",crisno3,"_",sentence_number_int_aligned3,"_",event_number_int)) %>%
                    dplyr::select(-crisno3, -sentence_number_int_aligned3) %>%
                    dplyr::arrange(crisno, sentence_number_int, event_number_int) %>%

@@

Save icb_long_clean!
```{r}
saveRDS(icb_long_clean_final, paste0(here::here(), "/replication_data/temp/ICBe_V1_long_clean.Rds"))

@@

saveRDS(icb_wide_clean, paste0(here::here(), "/replication_data/temp/ICBe_V1_wide_clean.Rds"))

### 2022-02-04 replication_data/rmd/03_aggregation.Rmd
input datas
Consolidated save files, names, and locations

icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/icb_long_clean.Rds"))

@@

Iterate and visualize sentences until convinced the translation is right

codings_wide_agreed_labeled_sample_ft <- 
      codings_wide_agreed_pruned_labeled %>%
                group_by(crisno, sentence_number_int_aligned, crisno_sent, sentence) %>%
                summarize(codings_sentence = paste(codings_sentence, collapse="\n")) %>%
                dplyr::select(crisno_sent, sentence, codings_sentence)  %>%
                dplyr::filter(codings_sentence!="No events.") %>%
                group_by(crisno) %>%
                sample_n(size=1) %>%
                ungroup() %>%
                dplyr::select(crisno_sent, sentence, codings_sentence) %>%
                as_flextable() %>%
                colformat_md() %>% 
                flextable::fontsize(size = 7, part = "all") %>%
                flextable::bg( i = which( 1:nrow(codings_wide_agreed_pruned_labeled) %% 2 == 1)  , j=1:ncol(events_df), part = "body", bg = "#EFEFEF") %>%
                flextable::width(j = 1, width=0.3, unit = "in") %>%
                flextable::width(j = 2, width=3, unit = "in") %>%
                flextable::width(j = 3, width=3, unit = "in")

codings_wide_agreed_labeled_sample_ft  %>% saveRDS(paste0(here::here(), '/replication_paper/tables/codings_wide_agreed_labeled_sample_ft.Rds'))
codings_wide_agreed_labeled_sample_ft

@@

saveRDS(codings_long, paste0(here::here(), "/replication_data/temp/codings_long.Rds")) 
saveRDS(codings_long_agreement, paste0(here::here(), "/replication_data/temp/codings_long_agreement.Rds"))

saveRDS(codings_long_agreed, paste0(here::here(), "/replication_data/out/codings_long_agreed.Rds")) 
saveRDS(codings_wide_agreed_pruned_labeled, paste0(here::here(), "/replication_data/out/codings_wide_agreed.Rds"))

>>>>

icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/ICBe_V1_long_clean.Rds"))

@@

@@

saveRDS(codings_long_agreement, paste0(here::here(), "/replication_data/out/ICBe_V1_long_agreement.Rds")) 
saveRDS(codings_long_agreed, paste0(here::here(), "/replication_data/out/ICBe_V1_long_agreed.Rds")) 
saveRDS(codings_wide_agreed_pruned_labeled, paste0(here::here(), "/replication_data/out/ICBe_V1_wide_agreed.Rds"))

### 2022-02-04 replication_paper/IntroducingICBe_DouglassEtAl_2021_BetaDraft_bookdown.Rmd
Consolidated save files, names, and locations

codings_wide_agreed <- readRDS(file=paste0(here::here(),'/replication_data/out/codings_wide_agreed.Rds'))
codings_long_agreed <- readRDS( paste0(here::here(), '/replication_data/out/codings_long_agreed.Rds'))
icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/icb_long_clean.Rds"))
icb_wide_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/icb_wide_clean.Rds"))

@@

```{r include=F}
#Load the ICB wide codings
icb_wide_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/icb_wide_clean.Rds"))

@@

```{r include=FALSE}
icb_wide_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/icb_wide_clean.Rds"))
n_crisis <- icb_wide_clean %>% dplyr::select(crisno) %>% unique() %>% nrow()
n_sentences <- icb_wide_clean %>% dplyr::select(crisno, sentence_number_int_aligned) %>% unique() %>% nrow()
n_events <- icb_wide_clean %>% dplyr::filter(event_number_int %in% c(1,2,3)) %>% nrow()
n_events_cuba <- icb_wide_clean %>% dplyr::filter(crisno == 196 & event_number_int %in% c(1,2,3)) %>% nrow()
n_coders <- icb_wide_clean %>% dplyr::select(email_id) %>% unique() %>% nrow()

@@

```{r, eval=T}
icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/icb_long_clean.Rds"))

codings_long_agreement <- readRDS(file=paste0(here::here(),  '/replication_data/temp/codings_long_agreement.Rds'))

@@

One form of internal validity for these codings is high agreement between coders when applying the ontology. We employ three ways to evaluate and maximize agreement: (1) multiple expert and novice coders per sentence (often including a tie-breaking expert coder where there were disagreements), (2) a theoretically motivated scheme for aggregating across disagreements, and (3) survey questions on self-reported confidence and reasons for low confidence. The unit of analysis for these comparisons is the individually applied tag; every answer to every question in the ontology is a separate tag applied to that sentence (e.g., an actor, a behavior, a date, etc.). There were `r icb_long_clean %>% pull(email_id) %>% unique() %>% length()` coders (including `r icb_long_clean %>% filter(email_id %>% str_detect("expert")) %>% pull(email_id) %>% unique() %>% length()` expert coders) who recorded `r icb_long_clean %>% nrow() %>% scales::comma()` coder-tags across the entire corpus. Of those, there were `r codings_long_agreement %>% filter(value_normalized!='') %>% nrow() %>% scales::comma()` unique sentence-tags applied by at least one coder. We ask how much support those possible tags received across coders, and how we should adjudicate disagreements when a tag was not chosen by every coder.

>>>>

icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/ICBe_V1_long_clean.Rds"))
icb_wide_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/ICBe_V1_wide_clean.Rds"))
codings_long_agreement <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1_long_agreement.Rds") )
codings_long_agreed <- readRDS( paste0(here::here(), '/replication_data/out/ICBe_V1_long_agreed.Rds'))
codings_wide_agreed <- readRDS(file=paste0(here::here(),'/replication_data/out/ICBe_V1_wide_agreed.Rds'))

@@

```{r include=F}
#Load the ICB wide codings

@@

```{r include=FALSE}

@@

```{r, eval=T}

@@

One form of internal validity for these codings is high agreement between coders when applying the ontology. We employ three ways to evaluate and maximize agreement: (1) multiple expert and novice coders per sentence (often including a tie-breaking expert coder where there were disagreements), (2) a theoretically motivated scheme for aggregating across disagreements, and (3) survey questions on self-reported confidence and reasons for low confidence. The unit of analysis for these comparisons is the individually applied tag; every answer to every question in the ontology is a separate tag applied to that sentence (e.g., an actor, a behavior, a date, etc.). There were 113 coders (including 5 expert coders) who recorded `r icb_long_clean %>% nrow() %>% scales::comma()` coder-tags across the entire corpus. Of those, there were `r codings_long_agreement %>% filter(value_normalized!='') %>% nrow() %>% scales::comma()` unique sentence-tags applied by at least one coder. We ask how much support those possible tags received across coders, and how we should adjudicate disagreements when a tag was not chosen by every coder.

### 2022-02-04 replication_paper/rmd/ICBEdataset_figure_metro_maps.Rmd
Consolidated save files, names, and locations

@@

icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_paper/data/in/icb_long_clean.Rds"))

@@

codings_long <- readRDS( paste0(here::here(), "/replication_paper/data/in/codings_long.Rds")) 
codings_long_agreement <- readRDS( paste0(here::here(), "/replication_paper/data/in/codings_long_agreement.Rds")) 
codings_long_agreed <- readRDS( paste0(here::here(), "/replication_paper/data/in/codings_long_agreed.Rds")) 
codings_wide_agreed <- readRDS( paste0(here::here(), "/replication_paper/data/in/codings_wide_agreed.Rds"))

>>>>

icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/ICBe_V1_long_clean.Rds"))
icb_wide_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/ICBe_V1_wide_clean.Rds"))
codings_long_agreement <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1_long_agreement.Rds") )
codings_long_agreed <- readRDS( paste0(here::here(), '/replication_data/out/ICBe_V1_long_agreed.Rds'))
codings_wide_agreed <- readRDS(file=paste0(here::here(),'/replication_data/out/ICBe_V1_wide_agreed.Rds'))

@@

@@

### 2022-02-04 replication_paper/rmd/ICBEdataset_figure_semantic_embeddings.Rmd
Consolidated save files, names, and locations

@@

codings_wide_agreed <- readRDS( paste0(here::here(), "/replication_paper/data/in/codings_wide_agreed.Rds")) 
codings_long_agreed <- readRDS( paste0(here::here(), "/replication_paper/data/in/codings_long_agreed.Rds")) 
icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_paper/data/in/icb_long_clean.Rds")) 
codings_long <- readRDS( paste0(here::here(), "/replication_paper/data/in/codings_long.Rds")) 
codings_long_agreement <- readRDS( paste0(here::here(), "/replication_paper/data/in/codings_long_agreement.Rds"))

@@

#devtools::install_github("ropenscilabs/umapr")
library(umapr)
embedding <- umapr::umap(sentences_embeddings)

@@

codings_long_agreed <- readRDS( paste0(here::here(), "/replication_paper/data/in/codings_long_agreed.Rds")) 
codings_long_agreed_embeded <- codings_long_agreed %>% ungroup() %>% left_join(sentences_embeded)

@@

codings_wide_agreed <- readRDS(paste0(here::here(), '/replication_paper/data/in/codings_wide_agreed.Rds'))
codings_wide_agreed_embeded <- codings_wide_agreed %>% dplyr::ungroup() %>% dplyr::left_join(sentences_embeded)

@@

library(RColorBrewer)
brewer_pal_info_df <- brewer.pal.info %>% dplyr::add_rownames( var = "rowname") %>% dplyr::arrange()
brewer_list <- list() 
for(i in c(11, 1:nrow(brewer_pal_info_df))){
  brewer_list[[as.character(i)]] <- brewer.pal(n=brewer_pal_info_df$maxcolors[i], brewer_pal_info_df$rowname[i])
}
posible_colors <- unlist(brewer_list) %>% unique(brewer_list)  #%>% sample()
posible_colors <- posible_colors[! posible_colors %in% c("#FFFFFF", "#FFFF99", "#E6F598", "#E0E0E0")] # drop white

value_normalized=codings_long_agreed_embeded_subset$value_normalized %>% unique() %>% as.factor()
value_normalized_colors = posible_colors[1:length(value_normalized)] #ok so pick a brewer pallet with lots of values and then assign it to specific values
names(value_normalized_colors) = levels(value_normalized)

@@

library(ggplot2)
p_semantic_embeddings <-
      codings_long_agreed_embeded_subset %>%
      ggplot(aes(x=UMAP1,y=UMAP2, color=value_normalized )) +
        geom_point(size=0.5, alpha=0.5) + 
        geom_text(data=sampled, aes(x=UMAP1, y=UMAP2, label=crisno_sent), color='black',size=1.5) +

        facet_wrap( ~ variable_normalized) + 
        theme_bw() +
        theme(legend.position = "none") + 
        geom_label(data=subset(value_means, label==1),
                   aes(x=UMAP1,y=UMAP2, fill = value_normalized, 
                       label=value_normalized, size=50), size = 3, inherit.aes=F, # #variable_normalized_count
                   colour = "white", fontface = "bold", label.padding = unit(0.1, "lines")) + 
        labs(
            title = "Variation in Tags by Semantic Embeddings of Source Sentences",
            subtitle = "Sentences Embedding Sentence-BERT, UMAP Projection ",
            caption = ""
        ) +
       scale_color_manual(values = value_normalized_colors) +
       scale_fill_manual(values = value_normalized_colors)

>>>>

#Load it here before the python reticulate business
#devtools::install_github("ropenscilabs/umapr")
library(umapr)

@@

icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/ICBe_V1_long_clean.Rds"))
icb_wide_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/ICBe_V1_wide_clean.Rds"))
codings_long_agreement <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1_long_agreement.Rds") )
codings_long_agreed <- readRDS( paste0(here::here(), '/replication_data/out/ICBe_V1_long_agreed.Rds'))
codings_wide_agreed <- readRDS(file=paste0(here::here(),'/replication_data/out/ICBe_V1_wide_agreed.Rds'))

@@

embedding <- umapr::umap(sentences_embeddings)

@@

codings_long_agreed_embeded <- codings_long_agreed %>% ungroup() %>% left_join(sentences_embeded)

@@

codings_wide_agreed_embeded <- codings_wide_agreed %>% dplyr::ungroup() %>% dplyr::left_join(sentences_embeded)

@@

library(RColorBrewer)
brewer_pal_info_df <- brewer.pal.info %>% dplyr::add_rownames( var = "rowname") %>% dplyr::arrange() %>% filter(category %in% "qual" & rowname %in% c('Dark2','Set2','Paired','Accent','Set1'))
brewer_list <- list() 
for(i in 1:nrow(brewer_pal_info_df)){
  brewer_list[[as.character(i)]] <- brewer.pal(n=brewer_pal_info_df$maxcolors[i], brewer_pal_info_df$rowname[i])
}
posible_colors <- unlist(brewer_list) %>% unique(brewer_list)  #%>% sample()
posible_colors <- posible_colors[! posible_colors %in% c("#FFFFFF", "#FFFF99", "#E6F598", "#E0E0E0", "#FFD92F","#FFFF33")] # drop white

value_normalized= codings_long_agreed_embeded_subset %>% count(value_normalized) %>% arrange(desc(n)) %>% filter(n>100) %>% pull(value_normalized) %>% factor()
value_normalized_colors = posible_colors[1:length(value_normalized)] #ok so pick a brewer pallet with lots of values and then assign it to specific values
names(value_normalized_colors) = as.character(value_normalized)

@@

library(ggplot2)
p_semantic_embeddings <-
      codings_long_agreed_embeded_subset %>%
      ggplot(aes(x=UMAP1,y=UMAP2, color=value_normalized )) +
        geom_point(size=0.5, alpha=0.5) + 
        geom_text(data=sampled, aes(x=UMAP1, y=UMAP2, label=crisno_sent), color='black',size=1.5) + 
        facet_wrap( ~ variable_normalized) + 
        theme_bw() +
        theme(legend.position = "none") + 
        geom_label(data=subset(value_means, label==1),
                   aes(x=UMAP1,y=UMAP2, fill = value_normalized, 
                       label=value_normalized, size=50), size = 3, inherit.aes=F, # #variable_normalized_count
                   colour = "white", fontface = "bold", label.padding = unit(0.1, "lines")) + 
        labs(
            title = "Variation in Tags by Semantic Embeddings of Source Sentences",
            subtitle = "Sentences Embedding Sentence-BERT, UMAP Projection ",
            caption = ""
        ) +
       scale_color_manual(values = value_normalized_colors) +
       scale_fill_manual(values = value_normalized_colors)

### 2022-02-04 replication_paper/rmd/ICBEdataset_paper_PlotInterCoderAgreement.Rmd
Consolidated save files, names, and locations

```{r}
icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/data/in/icb_long_clean.Rds")) 
codings_long <- readRDS(paste0(here::here(), '/replication_data/data/in/codings_long.Rds'))
codings_long_agreement <- readRDS( paste0(here::here(), '/replication_data/data/in/codings_long_agreement.Rds'))
codings_long_agreed <- readRDS( paste0(here::here(), '/replication_data/data/in/codings_long_agreed.Rds'))
codings_wide_agreed <- readRDS( paste0(here::here(), '/replication_data/data/in/codings_wide_agreed.Rds'))

>>>>

```{r}
icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/ICBe_V1_long_clean.Rds"))
icb_wide_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/ICBe_V1_wide_clean.Rds"))
codings_long_agreement <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1_long_agreement.Rds") )
codings_long_agreed <- readRDS( paste0(here::here(), '/replication_data/out/ICBe_V1_long_agreed.Rds'))
codings_wide_agreed <- readRDS(file=paste0(here::here(),'/replication_data/out/ICBe_V1_wide_agreed.Rds'))

### 2022-02-04 replication_paper/rmd/ICBEdataset_paper_appendixICBCrises.Rmd
Consolidated save files, names, and locations

@@

```{r include=F}
# #Load the ICB wide codings
icb_wide_clean <- readRDS(file=paste0(here::here(), "/replication_paper/data/in/icb_wide_clean.Rds"))
n_crisis <- icb_wide_clean %>% dplyr::select(crisno) %>% unique() %>% nrow()
n_sentences <- icb_wide_clean %>% dplyr::select(crisno, sentence_number_int_aligned) %>% unique() %>% nrow()
n_events <- icb_wide_clean %>% dplyr::filter(event_number_int %in% c(1,2,3)) %>% nrow()
n_events_cuba <- icb_wide_clean %>% dplyr::filter(crisno == 196 & event_number_int %in% c(1,2,3)) %>% nrow()
n_coders <- icb_wide_clean %>% dplyr::select(email_id) %>% unique() %>% nrow()

>>>>

# #Load the ICB wide codings
icb_wide_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/ICBe_V1_wide_clean.Rds"))

@@

```{r include=F}
n_crisis <- icb_wide_clean %>% dplyr::select(crisno) %>% unique() %>% nrow()
n_sentences <- icb_wide_clean %>% dplyr::select(crisno, sentence_number_int_aligned) %>% unique() %>% nrow()
n_events <- icb_wide_clean %>% dplyr::filter(event_number_int %in% c(1,2,3)) %>% nrow()
n_events_cuba <- icb_wide_clean %>% dplyr::filter(crisno == 196 & event_number_int %in% c(1,2,3)) %>% nrow()
n_coders <- icb_wide_clean %>% dplyr::select(email_id) %>% unique() %>% nrow()

### 2022-02-04 replication_paper/rmd/ICBEdataset_paper_figure_prep.Rmd
Consolidated save files, names, and locations

```{r, eval=T, echo=F, results='hide', include=T, message=F, cache=F, warning=F,  ft.arraystretch=0.75, fig.width=6, fig.height=6}
#ICBe  196
library(ggplot2)
p_phoenix_metro_plot_196 <- readRDS(file=paste0(here::here(), '/replication_paper/figures/metro_plots/p_phoenix_metro_plot_196.Rds'))
actor_colors <- p_phoenix_metro_plot_196$actor_colors

>>>>

```{r, eval=T, echo=F, results='hide', include=T, message=F, cache=F, warning=F,  ft.arraystretch=0.75, fig.width=6, fig.height=6}
#ICBe  196
library(ggplot2)
p_metro_plot <- readRDS(file=paste0(here::here(), '/replication_paper/figures/metro_plots/p_phoenix_metro_plot_196.Rds'))
actor_colors <- p_phoenix_metro_plot_196$actor_colors
